\section{Features (Simple English)}

This section lists what \watchdog{} does (and what it is planned to do) using simple, non-jargon language.

\subsection{Ingestion and Normalization}
\begin{itemize}
  \item Accept logs and metrics over HTTP from external producers.
  \item Validate the incoming payload (required fields, supported kinds, size limits).
  \item Normalize the event shape so downstream services see consistent fields.
  \item Classify incoming data as either a \emph{log} (reactive) or a \emph{metric} (proactive).
  \item Provide health endpoints so operators can verify the service is up.
\end{itemize}

\subsection{Incident (Ticket) Management}
\begin{itemize}
  \item Create an incident ticket when a critical condition is detected.
  \item Track ticket status through a small lifecycle: \texttt{OPEN} $\rightarrow$ \texttt{INVESTIGATING} $\rightarrow$ \texttt{RESOLVED}.
  \item List and fetch tickets so an operator can see what is happening.
  \item Allow an operator to manually update a ticket (status and notes/comments).
\end{itemize}

\subsection{Rules and Proactive Alerts}
\begin{itemize}
  \item Evaluate metrics against thresholds (for example, ``error rate too high'').
  \item Reduce noise by suppressing duplicates and ignoring low-signal events (roadmap).
  \item Support backpressure so bursts of data do not overwhelm the system (roadmap).
\end{itemize}

\subsection{NLP Enrichment (Intelligence Layer)}
\begin{itemize}
  \item Analyze log text and return: category (example: database), severity, confidence score, and extracted keywords/entities.
  \item Support a basic heuristic mode today and model-backed inference later.
\end{itemize}

\subsection{Security and Access Control}
\begin{itemize}
  \item Protect management APIs with authentication (JWT in the current starter; real JWT validation and RBAC are planned).
  \item Keep health checks unauthenticated for infrastructure probes.
  \item Plan for secure service-to-service calls (mTLS / service identity) once traffic patterns stabilize.
\end{itemize}

\subsection{Observability and Operations}
\begin{itemize}
  \item Emit logs and basic health endpoints from each service.
  \item Plan for metrics endpoints compatible with Prometheus and dashboards in Grafana.
  \item Plan for tracing and correlation IDs across services.
\end{itemize}

\subsection{User Interface (Roadmap)}
\begin{itemize}
  \item Provide a real-time dashboard to view active tickets and recent events (roadmap).
  \item Provide admin screens for user management and configuration (roadmap).
\end{itemize}

